### 2016-02-09 inputs/conclusions.tex
integrating notes from Fil+N pass

\section{Conclusions}
\label{sec:conclusions}
Imputation of missing genotypes can be an effective technique also for GBS data.
The most accurate imputation methods resulted in a total amount of wrongly imputed genotypes near to zero in rice and slightly over 10\% in alfalfa. 
The proportion of imputation errors, however, varied dramatically among genotype classes, approaching very high levels with the worst methods on the minor homozygous class.
The structure of the genome and the maturity of the reference assembly play a role in the imputation efficiency, as indicated by the greater efficiency obtained in rice compared with alfalfa and, most importantly, affected the relative efficiency of the methods. While Beagle was preferable for rice, general data imputation methods performed significantly better in the absence of a reference genome, such as in alfalfa. In particular, RFI and KNNI showed the lowest imputation errors in all classes, with KNNI to be preferred for computational efficiency.
The imputation accuracy tended to be relatively robust over increasing missing rates. However, KNNI showed a somewhat lower accuracy on high missingness scenarios, probably as a consequence of the ``curse of dimensionality''. In terms of computation requirements, all methods proved to be tractable over all problem complexities with a standard bioinformatics-lab computation infrastructure, except RFI (whose computational requirements increased exponentially with problem size and took up to 40 days with the complete rice dataset and maximum missing rate thresholds).\\
Exploring ways to improve imputation accuracy in GBS data, for instance by combining predictive methods as in boosting or model ensembling, while at the same time increasing algorithm efficiency to keep computation times reasonably low, is an important research area, and can help making low-cost genotyping-by-sequencing a very cost-effective technique for genomic applications in species with and without a reference genome.

>>>>

\section{Conclusions}
\label{sec:conclusions}
Imputation of missing genotypes can be an effective technique also for GBS data.
The most accurate imputation methods resulted in a total amount of wrongly imputed genotypes near to zero in rice and slightly over 10\% in alfalfa. 
The proportion of imputation errors, however, varied dramatically among genotype classes, approaching very high levels with the worst methods on the minor homozygous class.
The structure of the genome and the maturity of the reference assembly play a role in the imputation efficiency, as indicated by the greater efficiency obtained in rice compared with alfalfa. While Beagle was preferable for rice, general data imputation methods performed significantly better in the absence of a reference genome. In particular, in alfalfa RFI and KNNI showed the lowest imputation errors in all classes, with KNNI to be preferred for computational efficiency. The alignment of markers to closely related species can help, but comes at the price of discarding the non-aligning markers. Moreover, performances indicate that general methods are still the best option.\\
The imputation accuracy tended to be relatively robust over increasing missing rates. However, KNNI showed a somewhat lower accuracy on high missingness scenarios, probably as a consequence of the ``curse of dimensionality''. In terms of computation requirements, all methods proved to be tractable over all problem complexities with a standard bioinformatics-lab computation infrastructure, except RFI (whose computational requirements increased exponentially with problem size and took up to 40 days with the complete rice dataset and maximum missing rate thresholds).\\
Exploring ways to improve imputation accuracy in GBS data, for instance by combining predictive methods as in boosting or model ensembling, while at the same time increasing algorithm efficiency to keep computation times reasonably low, is an important research area, and can help making low-cost genotyping-by-sequencing a very cost-effective technique for genomic applications in species with and without a reference genome.

### 2016-02-09 inputs/discussion.tex
integrating notes from Fil+N pass

\subsection{Minor Allele Frequency and data (un)balancedness}
\label{sec:maf}
GBS data pose a greater challenge than SNP-array data to imputation algorithms, mainly as a consequence of the much larger quantity of missing genotypes they contain. On our data sets we found missing rates varied from 53\% to 67\%. With larger amounts of missing data the complexity of the imputation problem increases. Imputation error can have a negative impact on successive analyses (see for instance \cite{rutkoski_imputation_2013,Annicchiarico2015}).\\
The imputation of missing SNP genotypes is a special case of the broader family of classification problems: three-class missing genotypes (AA, AB and BB) at any given SNP locus are classified based on known genotypes at all remaining data points. Classification problems are known to be harder when data are unbalanced, i.e. the classes appear at different frequencies in the datasets, with typically one over-represented class
(see~\cite{kotsiantis_handling_2006}
and~\cite{sun_classification_2009} for a review). In SNP genotype imputation, data balancedness is directly related to the minor allele frequency (MAF). In the classification of unbalanced observations, it is important to look not only at the total classification accuracy, but also at the per-class accuracy. The total classification accuracy may be misleading, being ``dominated'' by the majority class
\cite{he_learning_2009}.
Indeed, we found that for most methods, even when the total classification accuracy was very high, relatively large error rates were present on minority classes. 
The dependency of imputation results on MAF has already been acknowledged  (e.g.,~\cite{hickey_factors_2012} in maize; \cite{ma_comparison_2013} in cattle; \cite{pei_analyses_2008} in humans). Our per-class dissection of results allowed a deeper insight into the imputation process. Indeed, all imputation algorithms performed considerably better in the majority class rather than in the less frequent classes.
In alfalfa, KNNI was easily the best imputation method in the heterozygous and minor homozygous classes, while SVDI and RFI performed only slightly better than MNI. In rice, Beagle gave the best imputation results, with accuracy close to 100\% both in the major and minor homozygous classes. MNI performed reasonably well in the alfalfa heterozygous class, with accuracy close 60\%, contributed to its moderately good results (total accuracy around 80\%).

@@

\subsection{Imputation efficiency: differences in rice vs. alfalfa}
\label{sec:role_of_species}
Imputation results were significantly different in rice and alfalfa: all imputation algorithms performed consistently better in rice data sets, where Beagle, RFI and KNNI achieved performances comparable to what is reported in literature for SNP-chip data (e.g.,~\cite{vanraden_genomic_2013} for bovine data;
\cite{the_1000_genomes_project_consortium_integrated_2012}
for human data). On the other hand, imputation accuracy in alfalfa data sets was much lower. This can be ascribed to four main factors: \\
i) the imputation problem was simpler in rice than in alfalfa, as the rice dataset comprised only pure lines, i.e. only two genotype classes instead of alfalfa's three; \\
ii) the genome structure was simpler in rice (diploid) than alfalfa (autotetraploid, rendered diploid ``in silico'' during SNP calling);\\
iii) alfalfa datasets did not contain population structure \cite{Annicchiarico2015}, while rice population was intrinsically stratified - being a collection of five subpopulation. Population structure is implicitly used by algorithms as Beagle and KNNI that create clusters of similar genotypes. Thus, rice dataset population structure facilitated the inputation process;\\
iv) rice data were analyzed by chromosome, allowing for higher average values of linkage disequilibrium (LD) among SNP markers, thus simplifying the imputation process.\\
Finally, the further difference in imputation accuracy between Alfalfa-Med and Alfalfa-PV suggests that other factors, directly connected to GBS protocols, may influence the general quality of the resulting data.\\
The most dramatic difference between data sets was found in FILLIN performances. The algorithm costantly produced 100\% uninputed results in alfalfa, while resulted in average performances in rice (albeit inferior to the other algorithms). This behaviour is probably due to FILLIN being designed to target inbred lines (as the name itself indicates).

@@

For alfalfa there is no reference genome sequenced yet. The genome of the close relative diploid \emph{Medicago Truncatula} is available \cite{young_medicago_2011} and could in principle be used. However, while the two genomes show high synteny \cite{li_saturated_2014}, aligning the SNPs on a genome of a different species (and with a different ploidity) would introduce a further level of complexity, and the effect of alignments errors would be hardly assessable. Moreover, the non-aligning SNPs would be discarded, not on the basis of data quality, but of local synteny. We therefore decided to not use the genome of \emph{M. Truncatula} in the present analysis.

In rice, where a reference genome is available, we could assess the effect of using ordered vs. unordered markers for imputation. Among the imputation methods used in this study, Beagle is the only one to make use of marker information, and was therefore tested with ordered and randomly reshuffled markers. Interestingly, with ordered markers Beagle shows astounding resilience to high missingness, with imputation accuracy in the minority class $>$ 0.95 even in the most extreme scenarios (70\% allowed, 20\% artificial missing genotypes).

Beagle worked substantially worse when the marker position was randomly reshuffled, with imputation accuracy in the minority class ranging from 0.75 (10\% allowed, 1\% artificial missing rates) to almost 0.5 (70\% allowed, 20\% artificial missing rates). When tested with alfalfa (with no marker position available) Beagle largerly overestimated by the majority class, performing poorly
This result confirmed that imputation methods specifically designed for ordered markers are not an option for species lacking a reference genome.

Previous studies, though not detailing a per-class breakdown of the imputation accuracy, provided interesting comparisons. In sugar beet, Biscarini et al.~\cite{biscarini_genome-enabled_2014} used Beagle to impute SNP-chip markers with partial within-chromosome/scaffold alignment, finding global accuracies ranging from 84\% to 80.9\% with 1\% to 20\% missing genotypes. Huang et al.~\cite{huang_efficient_2014} tested several algorithms, including Beagle, on simulated ordered GBS rice data with missing rates in the 30-60\% range and finding Beagle gave imputation accuracy consistently higher (+15-20\%) than KNNI. 
Finally, Swarts et al.~\cite{swarts_novel_2014} used ordered GBS maize data to compare Beagle with the FSFHap and FILLIN algorithms they developed. All these algorithms rely on a Hidden Markov Model (HMM) to detect recombination break-points between haplotypes. They mostly obtained high imputation accuracies in the three genotype classes, providing further evidence of the added value of having a reference genome assembly.

>>>>

\subsection{Minor Allele Frequency and data (un)balancedness}
\label{sec:maf}
GBS data pose a greater challenge than SNP-array data to imputation algorithms, mainly as a consequence of the much larger quantity of missing genotypes they contain. On our data sets we found missing rates varied from 53\% to 67\%. With larger amounts of missing data the complexity of the imputation problem increases. Imputation error can have a negative impact on successive analyses (e.g. on genomic predictions \cite{rutkoski_imputation_2013,Annicchiarico2015}).\\
The imputation of missing SNP genotypes is a special case of the broader family of classification problems: three-class missing genotypes (AA, AB and BB) at any given SNP locus are classified based on known genotypes at all remaining data points. Classification problems are known to be harder when data are unbalanced, i.e. the classes appear at different frequencies in the datasets, with typically one over-represented class
(see~\cite{kotsiantis_handling_2006}
and~\cite{sun_classification_2009} for a review). In SNP genotype imputation, data balancedness is directly related to the minor allele frequency (MAF). In the classification of unbalanced observations, it is important to look not only at the total classification accuracy, but also at the per-class accuracy. The total classification accuracy may be misleading, being ``dominated'' by the majority class
\cite{he_learning_2009}.
Indeed, we found that for most methods, even when the total classification accuracy was very high, relatively large error rates were present on minority classes. 
The dependency of imputation results on MAF has already been acknowledged  (e.g.,~\cite{hickey_factors_2012} in maize; \cite{ma_comparison_2013} in cattle; \cite{pei_analyses_2008} in humans). Our per-class dissection of results allowed a deeper insight into the imputation process. Indeed, all imputation algorithms performed considerably better in the majority class rather than in the less frequent classes.
In alfalfa, KNNI was easily the best imputation method in the heterozygous and minor homozygous classes, while SVDI and RFI performed only slightly better than MNI. In rice, Beagle gave the best imputation results, with accuracy close to 100\% both in the major and minor homozygous classes.

@@

\subsection{Imputation efficiency: differences in rice vs. alfalfa}
\label{sec:role_of_species}
Imputation results were significantly different in rice and alfalfa: all imputation algorithms performed consistently better in rice data sets, where Beagle, RFI and KNNI achieved performances comparable to what is reported in literature for SNP-chip data (e.g.,~\cite{vanraden_genomic_2013} for bovine data;
\cite{the_1000_genomes_project_consortium_integrated_2012}
for human data). On the other hand, imputation accuracy in alfalfa data sets was much lower. This can be ascribed to four main factors: \\
i) the imputation problem was simpler in rice than in alfalfa, since the rice dataset comprised only two genotype classes (AA and BB) instead of alfalfa's three (AA, AB, BB); \\
ii) rice is natively diploid while alfalfa, autotetraploid, has been rendered diploid ``in silico'' during SNP calling phase. This semplification step brought alfalfa dataset farther from biology;\\
iii) rice data were analyzed by chromosome, allowing for higher average values of linkage disequilibrium (LD) among SNP markers, thus simplifying the imputation process;\\
iv) rice markers were aligned on native genome, while alfalfa markers were aligned on a different species.

Alfalfa datasets did not present population structure \cite{Annicchiarico2015}, while rice population was intrinsically stratified - being a collection of five subpopulations. Population structure is implicitly used by algorithms like Beagle, FILLIN and KNNI, that create clusters of similar genotypes, and it is likely to affect imputation accuracy.\\
The most dramatic difference between datasets was found with FILLIN. The algorithm costantly produced 100\% uninputed results in alfalfa, while resulted in average performances in rice (albeit inferior to the other algorithms). This behaviour is probably due to FILLIN being designed to target inbred lines (as the name itself indicates).

@@

In rice, where a reference genome is available, we could assess the effect of using ordered vs. unordered markers for imputation. For alfalfa there is no reference genome sequenced yet. The genome of the close relative diploid \emph{Medicago Truncatula} is available \cite{young_medicago_2011} and can in principle used. However, while the two genomes show high synteny \cite{li_saturated_2014}, aligning on a different species (and with different ploidity) comes at the price of discarding those markers that do not align. \textcolor{red}{HOW MANY?}\\

Among the imputation methods used in this study, Beagle and FILLIN are the only ones that make use of marker information, and were therefore tested with ordered and randomly shuffled markers. In rice dataset with ordered markers Beagle showed astounding resilience to high missingness, with imputation accuracy in the minority class $>$95\% even in the most extreme scenarios (70\% allowed, 20\% artificial missing genotypes).
Beagle worked substantially worse when the marker position was randomly reshuffled, with imputation accuracy in the minority class ranging from 75\% (10\% allowed, 1\% artificial missing rates) to almost 50\% (70\% allowed, 20\% artificial missing rates). When tested with alfalfa Beagle largerly overestimated by the majority class and had very poor performances on heterozygous class. Shuffling marker positions further worsened the accuracy, and almost all missing data point assigned to the majority class.\\
FILLIN performances on rice follow the same pattern and worsen substantially when markers are shuffled. This result confirmed that imputation methods specifically designed for ordered markers are not an option for species lacking a reference genome.

Previous studies, though not detailing a per-class breakdown of the imputation accuracy, provide interesting comparisons. In sugar beet, Biscarini et al.~\cite{biscarini_genome-enabled_2014} used Beagle to impute SNP-chip markers with partial within-chromosome/scaffold alignment, finding global accuracies ranging from 84\% to 80.9\% with 1\% to 20\% missing genotypes. Huang et al.~\cite{huang_efficient_2014} tested several algorithms, including Beagle, on simulated ordered GBS rice data with missing rates in the 30-60\% range and finding Beagle gave imputation accuracy consistently higher (+15-20\%) than KNNI. 
Finally, Swarts et al.~\cite{swarts_novel_2014} used ordered GBS maize data to compare Beagle with the FSFHap and FILLIN algorithms they developed. They mostly obtained high imputation accuracies in the three genotype classes, providing further evidence of the added value of having a reference genome assembly.

### 2016-02-09 inputs/results.tex
integrating notes from Fil+N pass

\subsection{Genotypes}
\label{sec:genotypes}  
GBS detected 32\,706, 40\,734 and 166\,418 SNP loci in Alfalfa-PV, Alfalfa-Med and Rice, respectively (Table~\ref{tab:descriptive_statistics}). The overall missing rate was $66.6\%$, $59.6\%$ and $53.4\%$ in the three datasets. Supplementary Figure S1 shows the density distribution of missing rate per markers in the complete datasets. The amount of missing marker genotypes varied with the threshold of maximum per-marker missing-rate allowed in the data (10\%, 20\%, 40\% and 70\%) and the proportion of artificial missing genotypes that were introduced (1\%, 5\%, 10\% and 20\%). Missing data point counts ranged from a minimum of 3\,878 in Alfalfa-PV with 10\% allowed and 1\% artificial missing genotypes, to a maximum of 5\,580\,616 in Rice with 70\% allowed and 20\% artificial missing genotypes. Over all datasets and allowed/artificial missing genotypes thresholds, the amount of missing data points to be imputed averaged 249\,405.\\
Minor Allele Frequency (MAF) was 0.172, 0.170 and 0.140 in Alfalfa-PV, Alfalfa-Med and Rice, respectively. The three datasets were therefore unbalanced with respect to genotype classes: Rice had the lowest MAF, while Alfalfa-PV and Alfalfa-Med had the smallest minor classes (minor homozygotes 3.5\% and 3.2\% of the total genotypes). Figure~\ref{fig:genotype_classes} reports the proportion of genotypes in each class in the complete datasets (100\%) and as a function of the maximum allowed missing rate per marker. The relative proportion of genotype classes remained approximately stable in rice. In contrast, the heterozygous class in alfalfa tended to become smaller with increasing proportion of allowed genotypes. This reflected the different GBS calling criteria for homozygous and heterozygous SNP: heterozygous SNPs required fewer overlapping reads to be called, while the implemented quality filters on alfalfa required a larger number of reads to call a homozygous loci. The average missing-rate and MAF in the 12 rice chromosomes were comparable to the whole-rice dataset.
\textcolor{red}{
Alignment on reference genome assigned a position to 88.66\%, xxx\%, and xxx\% of Rice, Alfalfa-Med and Alfalfa-PV markers, respectively.
}

@@

\subsection{Imputation accuracy}
\label{sec:imputation_accuracy}  
\textcolor{red}{
\begin{itemize}
  \item all rice chromosome gave the same results, as in Suppl figures
  \item all numbers in this section need to be checked
  \item what about supplementary figures? still valid?
\end{itemize}
}
In rice, the average imputation accuracy over all genotypic classes was above 80\% for all methods. No significant difference was found between chromosome, thus results are presented averaged (Figure~\ref{fig:accuracy_rice}). \\
The overall accuracy for alfalfa, averaged across the two datasets, was 12-25\% lower than rice, ranging between 66\% and 84\% (Figure~\ref{fig:accuracy_alfalfa}). Again, since no significant difference was found between the two dataset, presented results are averaged (Figure~\ref{fig:accuracy_alfalfa}).

The imputation accuracy varied across the different genotype classes, with the highest accuracy in the most common genotype class (averaging 90.8\% and 99.3\% in alfalfa and rice, respectively), while the least common genotype class showed much lower accuracy (averaging 4.1\% and 73.4\% in alfalfa and rice, respectively).

Alfalfa datasets included heterozygous SNP loci, accounting for an average of 30\% of individuals per locus (Table~\ref{tab:descriptive_statistics}). Heterozygotes had an intermediate imputation accuracy ranging from 0\% with MNI to 70\% with KNNI. Results for each individual alfalfa population, the 12 individual rice chromosomes, and the whole rice dataset are similar to those discussed here (see Supplementary Figures S2 to S16).

Missing data did not affect the imputation accuracy substantially, with most algorithms showing a flat or almost flat response to increased missing rate. KNNI showed a decreasing imputation accuracy with increasing missing data, both in alfalfa and rice.

In rice, Beagle outperformed all other imputation methods, making efficient use of marker position (Figure~\ref{fig:accuracy_rice}). When markers were randomly reshuffled (thus offsetting position information), though, general imputation methods (other than MNI) showed a higher imputation accuracy than Beagle. The loss of performances on reshuffled markers is exacerbated on alfalfa datasets, and in particular on heterozygous and minor homozygous classes.

Similarly, FILLIN resulted in a 5-10\% accuracy drop when marker positions were shuffled. FILLIN performances were in general lower than other methods due to the fraction of unimputed genotypes, here accounted as wrong imputation. FILLIN did not impute an average of 14.6\% missing data in Rice and practically the entirety of Alfalfa data. Even trying to relax FILLIN constraint parameters, it was impossible to obtain any sensible result.

In general we observed for all thresholds and in both genotype classes the following ranking of methods for imputation accuracy: RFI $>$ KNNI $>$ SVDI.
In Rice, for 70\% allowed missing rate datasets, the imputation accuracy of RFI was still greater than 90\%, while it dropped towards 75\% for KNNI and SVDI. As expected, MNI had an imputation accuracy of 100\% in the major homozygous class, but dropped to 0\% in the minor homozygous class.\\
In alfalfa KNNI showed the highest imputation accuracy over all classes and in the heterozygous and minor homozygous genotype classes (Figure~\ref{fig:accuracy_alfalfa}). RFI and SVDI were second ranking. They did not differ much from MNI in the overall accuracy and in the major homozygous class, but gave higher imputation accuracy in the heterozygous and minor homozygous classes.

>>>>

\subsection{Genotypes}
\label{sec:genotypes}  
GBS detected 32\,706, 40\,734 and 166\,418 SNP loci in Alfalfa-PV, Alfalfa-Med and Rice, respectively (Table~\ref{tab:descriptive_statistics}). The overall missing rate was $66.6\%$, $59.6\%$ and $53.4\%$ in the three datasets. Supplementary Figure S1 shows the density distribution of missing rate per markers in the complete datasets. The amount of missing marker genotypes varied with the threshold of maximum per-marker missing-rate allowed in the data (10\%, 20\%, 40\% and 70\%) and the proportion of artificial missing genotypes that were introduced (1\%, 5\%, 10\% and 20\%). Missing data point counts ranged from a minimum of 3\,878 in Alfalfa-PV with 10\% allowed and 1\% artificial missing genotypes, to a maximum of 5\,580\,616 in Rice with 70\% allowed and 20\% artificial missing genotypes. Over all datasets and allowed/artificial missing genotypes thresholds, the amount of missing data points to be imputed averaged 249\,405.\\
Minor Allele Frequency (MAF) was 0.172, 0.170 and 0.140 in Alfalfa-PV, Alfalfa-Med and Rice, respectively. The three datasets were therefore unbalanced with respect to genotype classes: Rice had the lowest MAF, while Alfalfa-PV and Alfalfa-Med had the smallest minor classes (minor homozygotes 3.5\% and 3.2\% of the total genotypes). Figure~\ref{fig:genotype_classes} reports the proportion of genotypes in each class in the complete datasets (100\%) and as a function of the maximum allowed missing rate per marker. The relative proportion of genotype classes remained approximately stable in rice. In contrast, the heterozygous class in alfalfa tended to become smaller with increasing proportion of allowed genotypes. This reflected the different GBS calling criteria for homozygous and heterozygous SNP: heterozygous SNPs required fewer overlapping reads to be called, while the implemented quality filters on alfalfa required a larger number of reads to call a homozygous loci. Therefore homozygous loci tended to have higher missing rates, and to
be included progressively more with more relaxed thresholds on allowed missing level.
The average missing-rate and MAF in the 12 rice chromosomes were comparable to the whole-rice dataset.
\textcolor{red}{
Alignment on reference genome assigned a position to 88.66\%, xxx\%, and xxx\% of Rice, Alfalfa-Med and Alfalfa-PV markers, respectively.
}

@@

\subsection{Imputation accuracy}
\label{sec:imputation_accuracy}  
\textcolor{red}{
\begin{itemize}
  \item all rice chromosome gave the same results, as in Suppl figures
  \item all numbers in this section need to be checked
  \item what about supplementary figures? still valid?
\end{itemize}
}
In rice, the average imputation accuracy over all genotypic classes was above 80\% for all methods. No significant difference was found between chromosomes. Thus average accuracy over all chromosomes is therefore presented (Figure~\ref{fig:accuracy_rice}). \\
The overall accuracy for alfalfa, averaged across the two datasets, was 12-25\% lower than rice, ranging between 66\% and 84\%. No significant difference were found between the two datasets. Thus average accuracy over the Alfalfa-Med and Alfalfa-PV is presented (Figure~\ref{fig:accuracy_alfalfa}).

The imputation accuracy varied across the different genotype classes, with the highest accuracy in the most common genotype class (averaging \textcolor{red}{XXX}\% and \textcolor{red}{XXX}\% in alfalfa and rice, respectively), while the least common genotype class showed much lower accuracy (averaging \textcolor{red}{XXX}\% and \textcolor{red}{XXX}\% in alfalfa and rice, respectively).
Alfalfa datasets included heterozygous SNP loci, accounting for an average of 30\% of individuals per locus (Table~\ref{tab:descriptive_statistics}). Heterozygotes had an intermediate imputation accuracy ranging from 0\% with MNI to 70\% with KNNI. Results for each individual alfalfa population and the 12 individual rice chromosomes are similar to those discussed here (see Supplementary Figures S2 to S16). \\
Missing data did not affect the imputation accuracy substantially, with most algorithms showing a flat or almost flat response to increased missing rate. KNNI showed a decreasing imputation accuracy with increasing missing data, both in alfalfa and rice.

Beagle outperformed all other imputation methods in rice, making efficient use of marker position (Figure~\ref{fig:accuracy_rice}). When markers were randomly reshuffled (thus offsetting position information), though, general imputation methods (other than MNI) showed a higher imputation accuracy than Beagle. The accuracy loss with shuffled markers is exacerbated in alfalfa datasets, and in particular on heterozygous and minor homozygous classes.\\
Similarly, FILLIN resulted in a 5-10\% accuracy drop when marker positions were shuffled. FILLIN performances were in general lower than other methods due to the fraction of unimputed genotypes, here accounted as wrong imputation. FILLIN did not impute an average of 14.6\% missing data in Rice and practically the entirety of Alfalfa data. Even trying to relax FILLIN constraint parameters, it was impossible to obtain sensible results. Thus, FILLIN accuracy does not appear in Figure~\ref{fig:accuracy_alfalfa}.

When examining general imputation methods, resulting accuracies highlighted RFI and KNNI as the best ones. The two methods had comparable performances, without a preferable option over all experiments. SVDI followed, and MNI ranked last.\\
In Rice, for 70\% allowed missing rate datasets, the imputation accuracy of RFI was still greater than 90\%, while it dropped towards 75\% for KNNI and SVDI. As expected, MNI had an imputation accuracy of 100\% in the major homozygous class, but dropped to 0\% in the minor homozygous class.\\
In alfalfa KNNI showed the highest imputation accuracy over all classes \textcolor{red}{(XXX\%)} and in the heterozygous \textcolor{red}{(XXX\%)} and minor homozygous \textcolor{red}{(XXX\%)} genotype classes (Figure~\ref{fig:accuracy_alfalfa}). RFI and SVDI were second ranking. They did not differ much from MNI in the overall accuracy \textcolor{red}{(XXX\%)} and in the major \textcolor{red}{(XXX\%)} homozygous class, but gave higher imputation accuracy in the heterozygous \textcolor{red}{(XXX\%)} and minor homozygous \textcolor{red}{(XXX\%)} classes.
